---
title: ""
author: Ian Kretzler & Ben Marwick
date: Wednesday, Oct 30, 2014
output: html_document
---

## A Brief Case Study: Gender Research and the Role of Feminist Theory (Chacamool presentation)

Here we provide the code used to generate the figures in the 
presentation.

The data can be obtained freely from http://dfr.jstor.org/ 
We can share our data by request, but we're not sure that
the JSTOR terms of service allow us to post it publically. 

```{r setup}
# If you don't already have JSTORr, then  you need  to 
# download and install the package (do this only once ever per computer)
# uncomment and run the next two lines:
# library(devtools) # Windows users need Rtools, OSX users need XCode
# install_github("benmarwick/JSTORr")
library(JSTORr)
```


```{r get-data}
## The TOS for JSTOR DFR does not appear to allow redistribution of the data
## so we do not include it here. Please contact us if you'd like a copy and 
## we'll send it to you. You should be able to reproduce our dataset by
## searching JSTOR DFR and filtering 'Article Type' on 'Research article ' and 
## 'Miscellaneous', for each of the journal titles we used here.  

# five journals data
load("F:/My Documents/My UW/Research/1402 JSTOR text/corpus/five_journals.RData")
```


```{r}
JSTOR_2words(unpack_multi, "gender", c("feminism", "feminist"), span = 0.48, yearfrom = 1970)
ggsave("figure/2words_gender_feminism.png")
ggsave("figure/2words_gender_feminism.svg")
```

```{r}
JSTOR_2wordcor(unpack_multi,"gender",c("hunt","hunter","gatherer","gather","role","division","labor"), span = 0.5, yearfrom = 1970)
ggsave("figure/2words_gender_labor.png")
ggsave("figure/2words_gender_labor.svg")
```


```{r}
JSTOR_2wordcor(unpack_multi,"gender",c("intersectionality","race","queer","identity","intersectional","sexuality"), span = 0.6, yearfrom = 1970)
ggsave("figure/2words_gender_intersect.png")
ggsave("figure/2words_gender_intersect.svg")
```

### Some summary statistics on the words "gender", "feminist", and "feminism"

```{r}
feminism <- as.matrix(unpack_multi$wordcounts[,c("gender", "feminist", "feminism")])
# instances of the word
sum(feminism!=0)
# articles with the word
```

The total count of these words is `r colSums(feminism)`.

The number of articles containing these words is `r sum(feminism!=0)`

### Some summary statistics on the corpus used here

```{r}
journal_names <- gsub("\t", "", unique(unpack_multi$bibliodata$author)) # colnames are offset!
number_of_journals <- length(journal_names)
number_of_articles <- length(unique(unpack_multi$bibliodata$doi)) # colnames are offset!
```

The names of the journals in this corpus are `r journal_names`

The number of journals is `r number_of_journals`

The total number of articles is `r number_of_articles`

### Cluster analyses of articles containing the word 'gender'

```{r}
# these analyses were rather slow on my computer!
# subset to get only articles that have the word 'gender'
nouns <- JSTOR_dtmofnouns(unpack_multi, word = "gender", sparse = 1, POStag = TRUE)
# do cluster analysis 
gender_cluster <- JSTOR_clusterbywords(nouns, "gender", f = 0.01)
```





