---
title: ""
author: Ian Kretzler & Ben Marwick
date: Wednesday, Oct 30, 2014
output: html_document
---

## A Brief Case Study: Gender Research and the Role of Feminist Theory (Chacamool presentation)

Here we provide the code used to generate the figures in the presentation. This document is written is [rmarkdown](http://rmarkdown.rstudio.com/) and can be rendered into an HTML file containing the results of the analysis using `rmarkdown::render("chacmool.rmd")` or if you are using [RStudio](http://www.rstudio.com/) (as we do), then the "Knit" command (Ctrl+Shift+K) will render the document and display a preview of it.

The data can be obtained freely from http://dfr.jstor.org/ 
We can share our data by request, but we're not sure that the JSTOR terms of service allow us to post it publically. 

```{r setup}
knitr::opts_chunk$set(message=FALSE, warning=FALSE)
# If you don't already have JSTORr, then  you need  to 
# download and install the package (do this only once ever per computer)
# uncomment and run the next two lines:
# library(devtools) # Windows users need Rtools, OSX users need XCode
# install_github("benmarwick/JSTORr")
library(JSTORr)
```


```{r get-data}
## The TOS for JSTOR DFR does not appear to allow redistribution of the data
## so we do not include it here. Please contact us if you'd like a copy and 
## we'll send it to you. You should be able to reproduce our dataset by
## searching JSTOR DFR and filtering 'Article Type' on 'Research article ' and 
## 'Miscellaneous', for each of the journal titles we used here.  

# five journals data
load("G:/My Documents/My Papers/conferences/Chacmool2014/unpack_multi.RData")
```


```{r}
JSTOR_2words(unpack_multi, "gender", c("feminism", "feminist"), span = 0.48, yearfrom = 1970)
ggsave("figure/2words_gender_feminism.png")
ggsave("figure/2words_gender_feminism.svg")
```

```{r}
JSTOR_2wordcor(unpack_multi,"gender",c("hunt","hunter","gatherer","gather","role","division","labor"), span = 0.5, yearfrom = 1970)
ggsave("figure/2words_gender_labor.png")
ggsave("figure/2words_gender_labor.svg")
```


```{r}
JSTOR_2wordcor(unpack_multi,"gender",c("intersectionality","race","queer","identity","intersectional","sexuality"), span = 0.6, yearfrom = 1970)
ggsave("figure/2words_gender_intersect.png")
ggsave("figure/2words_gender_intersect.svg")
```

### Some summary statistics on the words "gender", "feminist", and "feminism"

```{r}
feminism <- as.matrix(unpack_multi$wordcounts[,c("gender", "feminist", "feminism")])
```

The total count of these words is `r colSums(feminism)`.

The number of articles containing these words is `r sum(feminism!=0)`

```{r}
# total count for each word?
no_gen_articles <- subset(feminism, feminism[,1] >0)
count_gender_articles <- length(no_gen_articles[,1]) # number of articles containing "gender"

no_feminist_articles <- subset(feminism, feminism[,2] >0)
count_feminism_articles <- length(no_feminist_articles[,2]) # number of articles containing "feminism"

no_feminism_articles <- subset(feminism, feminism[,3] >0)
count_feminist_articles <- length(no_feminism_articles[,3]) # number of articles containing "feminist"

# percent of articles containing 'gender' that also contain feminis*
gender_and_fem <- round((count_feminism_articles + count_feminist_articles) / count_gender_articles * 100, 0) 

# this number rises to what after 1984?
## first subset the data to 1984 and later...
bibliodata <- data.frame(doi = unpack_multi$bibliodata[ ,x],
                         year = as.numeric(unpack_multi$bibliodata[ ,year]),
                         stringsAsFactors = FALSE)
feminism <- data.frame(feminism)
feminism$doi <- rownames(feminism)
feminism_year <- merge(feminism, bibliodata, by =  'doi')
after_1984 <- feminism_year[feminism_year$year %in% 1982:1987, ]
## now compute percentage again...
after_1984_colsums <- data.frame(t(colSums(after_1984 != 0)))
after_1984_gender_and_fem <- round((after_1984_colsums$feminist + after_1984_colsums$feminism) / after_1984_colsums$gender * 100, 0)
```


Feminism appears in `r gender_and_fem`% of publications on gender; this number rises to `r after_1984_gender_and_fem`% for articles published during 1982-7 

### Some summary statistics on the corpus used here

```{r}
journal_names <- gsub("\t", "", unique(unpack_multi$bibliodata$author)) # colnames are offset!
number_of_journals <- length(journal_names)
number_of_articles <- length(unique(unpack_multi$bibliodata$doi)) # colnames are offset!
```

The names of the journals in this corpus are `r journal_names`

The number of journals is `r number_of_journals`

The total number of articles is `r number_of_articles`

### Cluster analyses of articles containing the word 'gender'

```{r, eval = FALSE}
# these analyses were rather slow on my computer!
# subset to get only articles that have the word 'gender'
nouns <- JSTOR_dtmofnouns(unpack_multi, word = "gender", sparse = 1, POStag = TRUE)
# do cluster analysis 
gender_cluster <- JSTOR_clusterbywords(nouns, "gender", f = 0.01)
gender_cluster
```


### Computational environment

This analysis was performed using R version `r getRversion()` and the following packages and versions: 

```{r}
sessionInfo()
```




